### 2015-11-30 fundamentals/impl.tex
takes @gidden suggestion about rewording.

Fleet-based, lumped-material models do not distinguish between discrete facility
entities or materials. However, some questions require resolution at the level
of individual facilities and materials. As a result, many detailed performance
metrics cannot be captured with previously existing fleet-based models. For 
example, to meaningfully optimize the cost and environmental impact of spent 
nuclear fuel storage, transport, and disposal strategies, discrete casks and 
their varying isotopic compositions must be taken into account.

>>>>

Fleet-based, lumped-material models do not distinguish between discrete facility
entities or materials. However, some questions require resolution at the level
of individual facilities and materials. As a result, many detailed performance
metrics cannot be captured with previously existing fleet-based models. For 
example, meaningful models of spent nuclear fuel storage transport, and
disposal strategies, require representation of discrete casks and their varying
isotopic compositions.
